\singlespacing \vspace{-2.5cm} \LARGE \textbf{Trade-offs among plant reproductive traits determine interactions with floral visitors}

### 2022-01-24 Main_Figures/Figure3_a.Rmd

pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
aes(x = -PC2, y = Interaction),size = 2.8, alpha=0.4) + geom_line(size=1.8)  + ylab("Interaction")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids"))+ scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

@@

pp2 + theme(legend.position = "bottom")

>>>>

pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__), group=guild, colour=guild)) + geom_point(data = dat_analysis,
aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
  theme_ms() + theme(legend.position = "none") + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids"))+ ggtitle("PC2", subtitle = "B") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

@@

pp1 + theme(legend.position = "bottom")

### 2022-01-24 Main_Figures/Global_trait_spectrum.Rmd

  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
     annotation_raster(style_l_1, xmin = 2.25, xmax = 3.05,ymin = 2.55, ymax = 3.7) +
    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 2, ymax = 4.7) +
    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
    annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
    annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2, ymax = -1.50) +
    annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)

@@

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
 plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,5.05,5.6,7.85,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.1,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
                         label = PCAloadings$Variables, color="black",fontface =2,size=4)

 plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,4.95,4.5,6.6,7.3,5.15)), y = (PCAloadings$PC2*c(3.83,6.4,5.7,7.4,-1,7.45)+c(0,0,0,0,-0.41,0)),
                         label =c("Low selfing", "Few flowers", "Small flowers", "Short styles", "Few ovules", "Short plants" ), color="black",fontface =2,size=4)

>>>>

  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
     annotation_raster(style_l_1, xmin = 2.10, xmax = 2.90,ymin = 2.55, ymax = 3.7) +
    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 2, ymax = 4.7) +
    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
    annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
    annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2, ymax = -1.50) +
    annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)

@@

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
 plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,4.95,5.6,7.45,7.2,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.2,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
                         label = PCAloadings$Variables, color="black",fontface =2,size=5)

 plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,4.95,4.5,6.6,7.2,5.15)), y = (PCAloadings$PC2*c(3.83,6.4,5.7,7.4,-1,7.45)+c(0,0,0,0,-0.41,0)),
                         label =c("Low selfing", "Few flowers", "Small flowers", "Short styles", "Few ovules", "Short plants" ), color="black",fontface =2,size=5)

### 2022-01-24 Main_Figures/Global_trait_spectrum_Qualitative_Vars.Rmd
Pollen nectar pPCA added

---
output:
  pdf_document: default
  html_document: default
---

@@

# Theme for publication
theme_ms <- function(base_size=12, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
      theme(text=element_text(color="black"),
            axis.title=element_text( size = rel(1.3)),
            axis.text=element_text(size = rel(1.75), color = "black"),
            legend.title=element_text(face="bold"),
            legend.text=element_text(),
            legend.background=element_rect(fill="transparent"),
            legend.key.size = unit(0.4, 'lines'),
            panel.border=element_rect(color="black",size=1),
            panel.grid.minor.x =element_blank(),
            panel.grid.minor.y= element_blank(),
             panel.grid.major= element_blank(),
            plot.title = element_text(size = rel(1.75), face="bold")
      ))
}

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.185, 0.13)) +ggtitle("(a)")

>>>>

---
output:
  pdf_document: default
  html_document: default
classoption: landscape

---

\pagenumbering{gobble}

@@

# Theme for publication
theme_ms <- function(base_size=12, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
      theme(text=element_text(color="black"),
            axis.title=element_text( size = rel(1.75)),
            axis.text=element_text(size = rel(1.75), color = "black"),
            legend.title=element_text(face="bold"),
            legend.text=element_text(size = rel(1.1)),
            legend.background=element_rect(fill="transparent"),
            legend.key.size = unit(0.4, 'lines'),
            panel.border=element_rect(color="black",size=1),
            panel.grid.minor.x =element_blank(),
            panel.grid.minor.y= element_blank(),
             panel.grid.major= element_blank(),
            plot.title = element_text(size = rel(2), face="bold")
      ))
}

@@

  plot <- plot + theme_ms() +ylim(-4,4) + xlim(-4,4) +  theme(legend.position = c(0.220, 0.130)) +ggtitle("A")

### 2022-01-24 Main_Figures/figure3_abcd.Rmd

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=14}

@@

p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+  xlab("High flower N.    Low flower N.\nSmall flowers    Large flowers")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",
  values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids"))+
  scale_y_log10()+ggtitle("D")
#Plot nicely PC2
ce_pc2 <- conditional_effects(analysis_1, effects = "PC2:guild",points=T)

p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Low poll. depend. High poll. depend.")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold")) + 
  scale_color_manual(name="Functional groups",values=c("orange", "black", 
  "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids")) + scale_y_log10()+ggtitle("E")

@@

pp2 + theme(legend.position = "bottom")

>>>>

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=17, fig.width=27}

@@

p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+  xlab("")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold")) + scale_color_manual(name="Functional groups",
  values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids"))+
  scale_y_log10()
#Plot nicely PC2
ce_pc2 <- conditional_effects(analysis_1, effects = "PC2:guild",points=T)

p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=guild, colour=guild)) + geom_point(data = dat_analysis,
  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+ xlab("")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0,face="bold")) + 
  scale_color_manual(name="Functional groups",values=c("orange", "black", 
  "limegreen","#E7298A", "cyan4","blueviolet"),labels=c("Bees","Coleoptera", "Lepidoptera", "Non-bee-Hymenoptera",
    "Non-syrphid-Diptera", "Syrphids")) + scale_y_log10()

@@

pp1+pp2+p1 +p2 + theme(legend.position = "none")+ plot_layout(ncol = 2)

### 2022-01-24 Manuscript/Lanuza_et_al_2021_Nat_Eco_Evo.tex

\begin{itemize}
\item
  1st explores is an ambiguous term. Maybe changing it for describe/determine? 2nd. Last phrase of the 1st paragraph lacks clarity. 3rd. Conceptual focus is unclear (3rd paragraph). General comment: What do we need to understand, and how will this information relate to broader problems in ecology/evolution? It is not sufficient to suggest that we need to improve our understanding without giving specifics regarding the impact of these studies.
\item
  There is insufficient justification/discussion of the traits used (Table 1). For example, what is the expected relevance of plant height? In addition, some of the traits are classified as both quantitative and qualitative. How can this work? For example, the selfing level was given as four categories of quantitative estimates as well as four categories of qualitative estimates. Aren't these the same thing? Finally, it is not clear why some traits were included, such as ovule number, whole others were not, such as flower color.
\item
  I am not convinced that the imputation process for missing trait values is accurate. There are many examples of very closely related plant species that differ dramatically in traits such as nectar volume and other traits relevant to pollinator interactions, so using a phylogenetic signal to estimate missing values may often give the wrong answer. In the Supplement you state: ``In general terms, nectar data was rarely present and we tried to minimise the loss of information by filling some species at family level.'' Seems preferable to simply exclude nectar as one of your traits.
\item
  A major issue with network data from studies of plant-visitor interactions is that there is rarely enough information to distinguish pollinators from pollen predators or nectar thieves.
\item
  It is not clear that the broad phylogenetic scale investigated in the paper is appropriate for investigating the importance of tradeoffs that evolve at the level of populations and species. I realize that the data at a finer micro-evolutionary scale are generally not available, but this is the level where constraints emerge.
\end{itemize}

>>>>

\begin{itemize}
\item
  1st explores is an ambiguous term. Maybe changing it for describe/determine? 2nd. Last phrase of the 1st paragraph lacks clarity. 3rd. Conceptual focus is unclear (3rd paragraph). General comment: What do we need to understand, and how will this information relate to broader problems in ecology/evolution? It is not sufficient to suggest that we need to improve our understanding without giving specifics regarding the impact of these studies.
\item
  There is insufficient justification/discussion of the traits used (Table 1). For example, what is the expected relevance of plant height? In addition, some of the traits are classified as both quantitative and qualitative. How can this work? For example, the selfing level was given as four categories of quantitative estimates as well as four categories of qualitative estimates. Aren't these the same thing? Finally, it is not clear why some traits were included, such as ovule number, whole others were not, such as flower color.
\item
  I am not convinced that the imputation process for missing trait values is accurate. There are many examples of very closely related plant species that differ dramatically in traits such as nectar volume and other traits relevant to pollinator interactions, so using a phylogenetic signal to estimate missing values may often give the wrong answer. In the Supplement you state: ``In general terms, nectar data was rarely present and we tried to minimise the loss of information by filling some species at family level.'' Seems preferable to simply exclude nectar as one of your traits.
\item
  A major issue with network data from studies of plant-visitor interactions is that there is rarely enough information to distinguish pollinators from pollen predators or nectar thieves.
\item
  It is not clear that the broad phylogenetic scale investigated in the paper is appropriate for investigating the importance of trade-offs that evolve at the level of populations and species. I realize that the data at a finer micro-evolutionary scale are generally not available, but this is the level where constraints emerge.
\end{itemize}

### 2022-01-24 Supplementary_Material/Analysis_2_Hymenoptera_Families_Separated.Rmd

theme_ms <- function(base_size=14, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(2)),
           axis.text=element_text(size = rel(1.8), color = "black"),
           legend.title=element_text(face="bold",size=rel(2)),
           legend.text=element_text(size=rel(1.4)),
           legend.background=element_rect(fill="transparent"),
           legend.key.size = unit(1.8, 'lines'),
           panel.border=element_rect(color="black",size=2.4),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank(),
           plot.title = element_text(hjust = 0.5,size=rel(2.75)),
           plot.subtitle = element_text(size=rel(2.5))
     ))
}

@@

pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("Interaction")+ xlab("")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(face="bold")) + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC1", subtitle = "(a)")+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

@@

pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(face="bold")) + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC2", subtitle = "(b)") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

@@

pp3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
 aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(face="bold")) + 
  scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC3", subtitle = "(c)")+ scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
#Plot nicely PC1
analysis_1 <- readRDS("r_bee_families.rds")
dat_analysis <- readRDS("dat_bee_families.rds")
########################################################################################################################

@@

p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+  xlab("High flower N.    Low flower N.\nSmall flowers    Large flowers")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0)) + scale_color_manual(name="Functional groups",
  values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+
  scale_y_log10()+ggtitle("(d)")
#Plot nicely PC2
ce_pc2 <- conditional_effects(analysis_1, effects = "PC2:bee_family",points=T)

p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Low poll. depend. High poll. depend.")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0)) + 
  scale_color_manual(name="Functional groups",values=c("orange", "black", 
  "limegreen","#E7298A", "cyan4","blueviolet")) + scale_y_log10()+ggtitle("(e)")

@@

p3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Short styles    Long styles\n Low selfing    High selfing")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.5),hjust = 0))+ 
  scale_color_manual(name="Functional groups",values=c("orange", 
  "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ scale_y_log10()+ggtitle("(f)")

>>>>

theme_ms <- function(base_size=14, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
     theme(text=element_text(color="black"),
           axis.title=element_text( size = rel(2.2)),
           axis.text=element_text(size = rel(1.85), color = "black"),
           legend.title=element_text(face="bold",size=rel(2.4)),
           legend.text=element_text(size=rel(1.8)),
           legend.background=element_rect(fill="transparent"),
           legend.key.size = unit(2, 'lines'),
           panel.border=element_rect(color="black",size=2.4),
           panel.grid.minor.x =element_blank(),
           panel.grid.minor.y= element_blank(),
           panel.grid.major= element_blank(),
           plot.title = element_text(hjust = 0.5,size=rel(2.95), face="bold"),
           plot.subtitle = element_text(size=rel(2.7),face="bold")))
}

@@

pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("Interaction")+ xlab("")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(face="bold")) + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC1", subtitle = "A")+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

@@

pp2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(face="bold")) + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC2", subtitle = "B") + scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

@@

pp3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
 aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("")+ xlab("")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(face="bold")) + 
  scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC3", subtitle = "C")+ scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))
#Plot nicely PC1
analysis_1 <- readRDS("r_bee_families.rds")
dat_analysis <- readRDS("dat_bee_families.rds")
########################################################################################################################

@@

p1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
  aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("Number of visits")+  xlab("High flower N.    Low flower N.\nSmall flowers    Large flowers")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.95),hjust = 0)) + scale_color_manual(name="Functional groups",
  values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+
  scale_y_log10()+ggtitle("D")
#Plot nicely PC2
ce_pc2 <- conditional_effects(analysis_1, effects = "PC2:bee_family",points=T)

p2 <- ggplot(ce_pc2[[1]], aes(x = -PC2, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
  aes(x = -PC2, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Low poll. depend. High poll. depend.")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.95),hjust = 0)) + 
  scale_color_manual(name="Functional groups",values=c("orange", "black", 
  "limegreen","#E7298A", "cyan4","blueviolet")) + scale_y_log10()+ggtitle("E")

@@

p3 <- ggplot(ce_pc3[[1]], aes(x = -PC3, y = (estimate__+1), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
  aes(x = -PC3, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5) + 
  ylim(0,quantile(dat_analysis$Interaction, 0.95)) + ylab("")+ xlab("Short styles    Long styles\n Low selfing    High selfing")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(size=rel(2.95),hjust = 0))+ 
  scale_color_manual(name="Functional groups",values=c("orange", 
  "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ scale_y_log10()+ggtitle("F")

### 2022-01-24 Supplementary_Material/Analysis_2_Hymenoptera_a.Rmd

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap= ""}

@@

pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("Interaction")+ xlab("")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(face="bold")) + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+ ggtitle("PC1", subtitle = "A")+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

@@

combined <- pp1 + pp2 + pp3 + p1 + p2 + p3 & theme(legend.position = "bottom")
combined_1 <- combined + plot_layout(guides = "collect",ncol = 3)

saveRDS(combined_1, "Plot_bee_families.rds")

combined_2 <- readRDS("Plot_bee_families.rds")

combined_2
```

>>>>

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10, fig.width=14,fig.pos = "!H",fig.cap= ""}

@@

pp1 <- ggplot(ce_pc1[[1]], aes(x = -PC1, y = (estimate__), group=bee_family, colour=bee_family)) + geom_point(data = dat_analysis,
aes(x = -PC1, y = Interaction),size = 2.5, alpha=0.4) + geom_line(size=1.5)  + ylab("Interaction")+ xlab("")+
  theme_ms() + theme(legend.position = "none",plot.title = element_text(face="bold")) + scale_color_manual(name="Functional groups",values=c("orange", "black", "limegreen","#E7298A", "cyan4","blueviolet"))+scale_y_continuous(breaks = c(0,  1), labels=c("No", "Yes"))

@@

pp1 + theme(legend.position = "bottom")

#combined <- pp1 + pp2 + pp3 + p1 + p2 + p3 & theme(legend.position = "bottom")
#combined_1 <- combined + plot_layout(guides = "collect",ncol = 3)

```
